---
title: "My Fun Day with RMarkdown"
author: "The Pi Gang"
date: "Wednesday, May 1, 2019"
---

<!-- this is a comment -->

```{css style-customizations,echo=FALSE}
h2 {
    font-size: 18px;
    color: red;
}
```

# First Section {#chosenID}

A single hashtag starts a section which should have an appropriate name. Adding some more text just to make this paragraph look longer so we can tell it's a paragraph when it renders. Notice that the entire paragraph is on line 9 (subject to change) of my document but wraps around for ease of reading.

Leaving a blank line creates a new paragraph.

# Second Section

You start a new section with a single hashtag without closing the previous section.

# Let's Talk About Subsections

In a structured document you probably want to have smaller sections within a section.

## First Subsection

Two hashtags opens a subsection within a section.

## Another Subsection

The heading here should look the same as the other subsections, because CSS style choices are applied universally, unless specifically overwritten.

# Lists

First of all, notice, that we exit subsections and sections simply by creating a new section. We don't close anything.

## Unordered Lists

- Blue
    - Royal
    - Navy
    - Sky
- Yellow
- Orange
- Red
- Purple

## Ordered Lists

1. New York
    a. Coal
    a. Gas
    a. Wood
1. New Jersey
    a. Gas
    a. Wood
1. Rome
1. Philadelphia
1. Detroit
1. Naples
1. New Haven

# Formatting

Surrounding text with _single underscores and no spaces_ creates emphasized text, which happens to look italic^[We can override this style using CSS.] with default settings.

Two __underscores__ will make strong text, which happens to look bold.

Backticks create `code style` text.

# Links

[My website](https://www.jaredlander.com)

This link goes to [our first section](#chosenID).

# R Time!!!!!!!!!!!!!

```{r simple-math}
1 + 1
2*3
```

Let's play with variables.

```{r variables}
x <- 3
x
```

Let's see if the `x` object is available in subsequent chunks.

```{r use-variables,echo=-1,eval=FALSE}
# comments in a chunk
x + 1
```

```{r show-options,results='hide'}
z <- 5
z*2
```

```{r show-z}
z
```

# Plots

```{r diamond-scatter,dev='png',fig.cap="Scatterplot of diamond price vs size, color coded by cut",cache=TRUE}
library(ggplot2)

ggplot(diamonds, 
       aes(x=carat, y=price, color=cut)) + 
    geom_point()
```

Now let's use that plot.

```{r show-caching,cache=TRUE,dependson=c('diamond-scatter')}
ggplot(diamonds, aes(x=price)) + 
    geom_histogram()
```

```{r read-tomato-data,cache=TRUE}
here::here()
getwd()
here::here('data', 'TomatoFirst.csv')
Sys.time()
tomato <- readr::read_csv(
    here::here('data', 'TomatoFirst.csv')
)
```

When we come back, we'll display the tabe of data and show how to cache based on the data changing.

```{r show-tomato,cache=TRUE,dependson=c('read-tomato-data')}

```

